Tampering Detection In Low-Power Smart Cameras

### 2015-05-22 paper.tex
sistemato piazzamento immagini (ho risparmiato una pagina!)
aggiunta tabella con AUC

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage[ruled]{algorithm2e}
%\usepackage[lined,boxed,commentsnumbered]{algorithm2e}
\usepackage{amssymb}
\usepackage{amsmath,graphicx,color,doi}
\usepackage{algorithm2e}
%\usepackage{algorithmic}	
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{cite}

@@

We here introduce a tampering-detection algorithm that has been specifically designed for low-power smart cameras: the algorithm leverages very simple indicators that are then monitored by an outlier-detection scheme. Any frame yielding anomalous indicator is detected as a tampering attempt. Core of the algorithm is the partitioning of the scene into adaptively defined regions, that are preliminarily defined by segmenting the image during the algorithm-configuration phase, and which shows to substantially improve the detection of camera displacements. Our experiments show that the proposed algorithm can successfully operate on sequences acquired at very low-frame rate, such as one frame every minute, and at a very small computational complexity. %and leveraging the image partitioning into regions yields improved performance with respect to monitoring the whole scene

@@

\begin{equation}
\label{eq:energyLuma}
l(t) = \mathcal{L}[z_t] =\frac{\sum_{\mathcal{X}} z_t(x) }{|\mathcal{X}|} ,
\end{equation}

\begin{equation}
\label{eq:gradientDetr}
\frac{\partial g}{\partial t}(t) = g(t) - g(t-1),
\end{equation}

\begin{equation}
\label{eq:lumaDetr}
\frac{\partial l}{\partial t}(t) = l(t) - l(t-1).
\end{equation}

FRAME DIFFERENCE:
\begin{equation}
	\label{eq:frameDiffReg}
	\varphi_k(t) = \frac{\sum_{x \in R_k}(z_t(x) - z_{t-1}(x))^2}{|R_k|}, k=1,\dots,K.
\end{equation}

@@

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{R_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{\mathcal{R}_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

@@

\begin{figure}

@@

\includegraphics[width=0.9\linewidth]{Immagini/sequenze}

@@

\begin{figure}

@@

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage[ruled]{algorithm2e}
%\usepackage[lined,boxed,commentsnumbered]{algorithm2e}
\usepackage{amssymb}
\usepackage{amsmath,graphicx,color,doi}
\usepackage{algorithm2e}
%\usepackage{algorithmic}	
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{cite}

@@

We here introduce a tampering-detection algorithm that has been specifically designed for low-power smart cameras: the algorithm leverages very simple indicators that are then monitored by an outlier-detection scheme. Any frame yielding anomalous indicator is detected as a tampering attempt. Core of the algorithm is the partitioning of the scene into adaptively defined regions, that are preliminarily defined by segmenting the image \ad{Giacomo: scene al posto di image??} during the algorithm-configuration phase, and which shows to substantially improve the detection of camera displacements. Our experiments show that the proposed algorithm can successfully operate on sequences acquired at very low-frame rate, such as one frame every minute, and at a very small computational complexity. %and leveraging the image partitioning into regions yields improved performance with respect to monitoring the whole scene

@@

%\begin{equation}
%\label{eq:energyLuma}
%l(t) = \mathcal{L}[z_t] =\frac{\sum_{\mathcal{X}} z_t(x) }{|\mathcal{X}|} ,
%\end{equation}  
%
%
%\begin{equation}
%\label{eq:gradientDetr}
%\frac{\partial g}{\partial t}(t) = g(t) - g(t-1),
%\end{equation}
%
%
%\begin{equation}
%\label{eq:lumaDetr}
%\frac{\partial l}{\partial t}(t) = l(t) - l(t-1).
%\end{equation}

FRAME DIFFERENCE:
\begin{equation}
	\label{eq:frameDiffReg}
	\varphi^k(t) = \frac{\sum_{x \in R_k}(z_t(x) - z_{t-1}(x))^2}{|R_k|}, k=1,\dots,K.
\end{equation}

@@

\begin{algorithm}[t]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{R_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{\mathcal{R}_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

@@

\begin{figure}[t]

@@

\includegraphics[width=1\linewidth]{Immagini/sequenze}

@@

\begin{figure}[htb]

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[tbh]
\begin{tabular}{l|l|l|l|l|l|l|}
\cline{2-7}
& \multicolumn{3}{l|}{\cellcolor[HTML]{C0C0C0}\textbf{Displacement Detection}}  & \multicolumn{3}{l|}{\cellcolor[HTML]{C0C0C0}\textbf{Defocus Detection}} \\ \cline{2-7} 
& \cellcolor[HTML]{EFEFEF}\textbf{Regions} & \cellcolor[HTML]{EFEFEF}\textbf{Total} & \cellcolor[HTML]{EFEFEF}\textbf{Voronoi} & \cellcolor[HTML]{EFEFEF}\textbf{Regions} & \cellcolor[HTML]{EFEFEF}\textbf{Total} & \cellcolor[HTML]{EFEFEF}\textbf{Voronoi} \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{Luma}}     & 0.9994 & 0.9989 & 0.9985  &            &            &             \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{Gradient}} &  		 &  		  &             & 0.9895 & 0.9996 & 0.9996  \\ \hline
\multicolumn{1}{|l|}{\cellcolor[HTML]{EFEFEF}\textbf{FD}}         & 0.9974 & 0.9944 & 0.9974  & 0.5526 & 0.5322 & 0.5391  \\ \hline
\end{tabular}
\caption{Area under curve of the analized solutions}
\label{tab:AUC}
\end{table}

Numero di operazioni richieste:
Calcolo di g(t):
\begin{itemize}
\item Norma gradiente: 196 FLOP per pixel
\item Media delle norme del gradiente
\end{itemize}
Calcolo di l(t):
\begin{itemize}
\item Media dei valori di grigio
\item Detrending: 1 FLOP per frame
\end{itemize}
Monitoraggio one-shot: 2 confronti
%Monitoraggio sequenziale: 
%Ogni 20 frame
%Calcolo intervalli di confidenza: ~70 FLOP
%Confronto tra intervalli di confidenza: 2 confronti
